---
title: "MasterLab"
author: "Group 2"
date: "01-03-2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First of all we pre-load every need package in order to use them later for our analysis.
```{r Environment Creating}
library(quantmod)
library(tidyverse)
library(tidyquant)
library(timetk)
library(readxl)
library(dplyr)
```

Below we are imported our collected inflation data set. We loaded therefore the monthly data set and the yearly data set. Regarding the yearly record, we only used it here for illustration purposes and for providing a short overview for the user. For our analysis we use the monthly stock data base and the monthly inflation. 

```{r Inflation Data Import}
Inflation_yearly <- read_excel("Inflation_Data_Europe.xls", sheet = "R_Export_yearly", col_types = c("date","numeric", "numeric", "numeric","numeric", "numeric", "numeric","numeric", "numeric", "numeric","numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric","numeric", "numeric", "numeric", "numeric", "numeric", "numeric","numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric","numeric", "numeric"))

Inflation_monthly <- read_excel("Inflation_Data_Europe.xls",sheet = "R_Export_monthly", col_types = c("date", "numeric", "numeric", "numeric","numeric", "numeric", "numeric", "numeric", "numeric", "numeric","numeric", "numeric", "numeric","numeric", "numeric", "numeric", "numeric", "numeric", "numeric","numeric", "numeric", "numeric","numeric", "numeric", "numeric","numeric", "numeric", "numeric"))

Inflation <- Inflation_monthly %>%
  dplyr::filter(date >= "2003-02-28",
          date <= "2021-06-30") %>%
          arrange(date)

europe_inf <- Inflation[c(1,5)] #hard-coded

STOXX_index <- read_excel("STOXX_600.xlsx", 
    sheet = "R_Export", col_types = c("date", 
        "numeric", "numeric", "numeric"))

stock <- dplyr::right_join(europe_inf, STOXX_index, by = "date")
```


```{r Implementation of the Stock Tickers}
Ticks_01 <- c("TREL-B.ST","RR.L","HSV.L","DRX.L","GFC.PA","0QVM.IL","AKBLF","GETI-B.ST","SSAB-B.ST","URW.AS","0F4I.IL","DIE.BR","0GWS.IL", "BOSS.DE","MOWI.OL","TRN.MI","AM.PA","DVDCF","NTGY.MC","OSB.L","ORSTED.CO","MT.AS","DLN.L","RHM.DE","CNA.L","OMV.VI","BLND.L","TEL2-B.ST","CAST.ST","ADP.PA","SAFE.L","NESTE.HE","FMS","SCHA.OL","DOCS.L","ADE.OL","PSO","TS","LAND.L","BYG.L","RPYTF","PUB.PA","IFX.DE","COV.PA","HM-B.ST","COL.MC","AMS.SW","RTO.L","SDF.DE","GLPEY","AED.BR","IMBBY","ABN.AS","DB1.DE","0NVV.IL","SGRO.L","5PP.F","ELI.BR","PHP.L","SNMRY","TTE","DUFN.SW","THLLY","NDA.DE","SGBAF","0RG8.IL","COFB.BR","AMP.VI","CLLNY","BBOX.L","ARZGY","DEO","III.L","BAYN.DE","TIIAY","WPP","ORK.OL","BESIY","JDSPY","FRE.DE","NXT.L","0DPU.IL","SECT-B.ST","0HV2.IL","IG.VI","AEGOF","UTG.L","EQNR","KOG.OL","IGG.L")

Ticks_02 <- c("MTX.DE","SHEL","BOL.ST","ACKB.BR","FINMY","WDP.BR","INF.L","TIGO","REPYY","UMG.AS","HELN.SW","RYAAY","KKPNY","SBB-B.ST","PSPN.SW","EZJ.L","BAKKA.OL","ENGGY","SOP.PA","RF.PA","SFOR.L","PSM.DE","EXXRF","SALM.OL","CAP.PA","0R4Y.IL","ATL.MI","DNOPY","BUD","UMI.BR","NOD.OL","NETC.CO","HSX.L","HOLM-B.ST","ADYEY","INVP.L","0N4Y.IL","FABG.ST","BG.VI","IAG.L","BEI.DE","BTI","RIO","LISN.SW","CA.PA","GLNCY","0RG6.IL","AT1.DE","MNG.L","TATE.L","E","0EWD.IL","IHG","DTE.DE","SRT3.DE","SPSN.SW","SEB-A.ST","ORP.PA","DEMANT.CO","DB","VIV.PA","ADS.DE","SAGA-B.ST","LUNE.ST","EOAN.DE","NGLOY","KGF.L","ABF.L","ENEL.MI","SKA-B.ST","MKS.L","SOBI.ST","KER.PA","TEG.DE","CTEC.L","TEF","0NMU.IL","WTB.L","MONRF","BA.L","ORA.VI","0GWB.IL","ACXIF","UBS","CDI.PA","SREN.SW","ASML","STM","ITX.VI","BRBY.L","TELIA1.HE","PAH3.DE","0MGU.IL","INDT.ST","CRDA.L","GBLB.BR","NENT-B.ST","BP","STMN.SW","SWED-A.ST","SFZN.SW","MUV2.DE","LIN","NGG","VIFN.SW","ULE.L","0N54.IL","BAMI.VI","RSH.HA","LIFCO-B.ST","BALD-B.ST","ENT.L")

Ticks_03 <- c("KOJAMO.HE","RNO.PA","BT-A.L","BVIC.L","VMUK.L","ROG.SW","DCC.L","WIS.DU","COLO-B.CO","LOGI","WIHL.ST","0RMT.IL","SGE.L","ALLN.SW","KINV-B.ST","UL","RBI.VI","RI.PA","AV.L","SAMPO.HE","LHA.DE","AKZOY","0RI5.IL","EMG.L","0ML1.IL","TUI1.DE","RUBSF","SCHN.SW", "SAP","BLHEF", "EN.PA", "KBCSY", "AUTO.OL","G24.DE","0RDV.IL","STAN.L", "SHB-A.ST", "VOD", "SCR.PA","BARN.SW","AKRBP.OL", "SPIE.PA", "UBI.PA", "SY1.DE", "ELISA.HE","FGR.PA", "BUCN.SW", "STRN", "CFRHF", "ALV.DE", "ADRNY","NVS","GMAB.CO", "KIND-SDB.ST", "LEG.DE","GALE.SW", "CCH.L","EBS.VI","BNZL.L","ERF.PA","BNR.DE","JDE.F","CAIXY","SIGN.SW","TSCO.L","SCMN.SW","2NN.F","0A8B.IL", "ZURN.SW", "NEXPF","DG.PA","AI.PA","BOIVF" , "MC.PA" , "EDEN.PA", "CBK.DE","STERV.HE","RYLPF","CS.PA","ISS.CO","UNCRY", "CBG.L","SCA-A.ST")

Ticks_04 <- c("ACS.MC", "ALIF-B.ST", "STLA.PA", "HEXA-B.ST", "AN3.F", "MBG.DE", "0KBZ.IL","MGGT.L", "AIR.PA", "P9O.F", "PNDORA.CO", "SBRY.L", "AVST.L", "ISP.VI","0EXG.IL", "CNP.PA","ML.PA","GRG.L", "AZN", "HNR1.DE", "SCT.L", "ERIC", "CS", "NOK", "LSEG.L", "SK3.IR", "AC.PA", "SSE.L" ,"PUM.DE", "EDPFY", "CRARY", "LATO-B.ST", "EVK.DE","SWMA.ST","UU.L", "0QVJ.IL", "BC8.DE", "TECN.SW", "WOSG.L", "QGEN","LONN.SW")

Ticks_05 <- c("REC.MI" , "DKSH.SW", "0NBD.IL" , "SNW.DE", "IBDRY", "ENGI.PA", "SOLB.BR", "SAF.PA", "BBVA", "0QVU.IL","ELUX-B.ST", "EVO.ST", "ADEN.SW", "SWGAY", "GSK", "ALCN.MX", "ARCAD.AS", "ANDR.VI", "HSBC", "0NZM.IL", "HEINY", "UPM.HE", "ELEZY", "TKA.DE","ALLFG.AS", "PGHN.SW", "ICP.L", "TRYG.CO", "INVE-B.ST", "VITR.ST", "BCDRF","0K9W.IL", "MB.MI", "INW.MI", "DLG.L", "SHL.DE" , "RWE.DE", "YAR.OL","TEL.OL", "SWEC-B.ST", "RMG.L", "VNA.DE", "AGS.BR", "OTGLY")

Ticks_06 <- c("DANSKE.CO", "AMADY", "TEP.PA", "SNN", "ASM.AS", "BKNIY", "INCH.L", "AAK.ST", "ROR.L","SFNXF", "0H13.IL", "HL.L", "TYRES.HE", "SLHN.SW", "STB.OL", "BVI.PA", "DSV.CO", "GET.PA", "HLMA.L", "HOLN.SW", "FNTN.DE", "CNHI","WIZZ.L","PNN.L", "CON.DE", "BEAN.SW", "VWAGY", "SPX.L", "ABDN.L", "RMV.L", "IWG.L" , "NSRGY" , "UCB.BR", "BCS" , "ARKAY" , "STOR-B.ST" , "RELX","ING" , "SK.PA")

Ticks_07 <- c("FORTUM.HE" , "ECM.L" , "BIRG.IR", "SECU-B.ST" , "FUTR.L" , "RBREW.CO", "MNDI.L" , "BANB.SW" , "ORNBV.HE", "0HB4.IL","RACE.VI","WIE.VI","CLN.SW","VWS.CO","TPK.L" , "BMW.DE", "0FMN.IL" , "CPG.L" , "SOON.SW", "JBAXY", "DPW.DE", "EXPN.L","AFX.DE","BNDSF" , "AMUN.PA", "MRK.DE", "VTAGY", "GNS.L", "DSRLF", "EQT.ST", "MRO.L", "SXS.L", "SDR.L","DOM.ST","0NY8.IL","ITV.L","NZYM-B.CO")

Ticks_08 <- c("UTDI.DE","CARL-B.CO","NEM.DE","BAS.DE","PDYPY","GL9.IR","ABB","ITRK.L","SMDS.L","VER.VI","UN01.DE","FPE.DE","SGO.VI","NIBE-B.ST","SIKA.SW", "HAS.L","0KFX.IL","0QP4.IL","HWDN.L","BEZ.L","WALL-B.ST","IPSEY","DNB.OL","KBX.DE","AHT.L","JMAT.L","DTG.DE","AMBU-B.CO","SGSN.SW","SIM.CO","VOE.VI", "ALE.WA","0RHS.IL")

Ticks_09 <- c("STJ.L","HEN3.DE","PZU.WA","AZA.ST","GFTU.L","CHR.CO","FLUIF","0RPR.IL","PRYMY","AALBF","EMSN.SW","PST.MI","SIE.DE","DPH.L", "AUTO.L","GLE.VI","ELIS.PA","QLT.L","SW.VI","EPI-B.ST","BPT.L","KESKOB.HE","WLN.PA","EVO","0QVF.IL","LYG","VLEEY","TKWY.AS","PRU.DE","LR.PA","LGEN.L","ZAL.DE", "NHYDY","WEIR.L","NWG","ATO.PA","0RUG.IL")

Ticks_10 <- c("NVO","FRRVY","RDSMY","PHNX.L","VCT.L","ADM.L","VACN.SW","KRZ.IR","IMI.L","HPOL-B.ST","CRH","GEBN.SW","HEI.DE","EL.PA","BKPKF","GN.CO","ASSA-B.ST","BNP.PA","HFG.DE","KHNGF","ADDT-B.ST","GIVN.SW","DPLM.L","OCDO.L","KNEBV.HE","VLVLY","BKG.L", "EDF.VI","ANTO.L","INRN.SW","1TY.DE" , "1COV.DE","LXS.DE", "KGHPF" , "SMIN.L" ,"KRX.IR","EVD.DE","VOLCAR-B.ST","ROCK-B.CO" , "MIPS.ST")

Ticks_11 <- c("ENR.DE" ,"LPP.WA" , "SINCH.ST", "BDEV.L", "EO.PA", "QTCOM.HE", "TEMN.SW","ALO.PA", "SU.PA", "RKT.L", "GAW.L", "HIK.L", "EKTA-B.ST", "ESSITY-B.ST","HUSQ-B.ST", "FERG" , "GJF.OL", "AVV.L", "BMRRY", "TW.L", "G1A.DE","LIGHT.AS", "M6Q.SG", "DHER.DE","WISE.L", "ONT.L","MRSK.VI","KGX.DE", "PSN.L","VALMT.HE", "ALFA.ST", "TOM.OL", "SAND.ST","BWY.L", "NDA-FI.HE", "ARGX", "VTY.L", "ATLC","THULE.ST", "SGRE.MC", "SKF-B.ST", "0IKJ.IL", "RAA.DE")
```

```{r Data Import of the individual stocks}
getSymbols(Symbols = Ticks_01, auto.assing = FALSE)
getSymbols(Symbols = Ticks_02, auto.assing = FALSE)
getSymbols(Symbols = Ticks_03, auto.assing = FALSE)
getSymbols(Symbols = Ticks_04, auto.assing = FALSE)
getSymbols(Symbols = Ticks_05, auto.assing = FALSE)
getSymbols(Symbols = Ticks_06, auto.assing = FALSE)
getSymbols(Symbols = Ticks_07, auto.assing = FALSE)
getSymbols(Symbols = Ticks_08, auto.assing = FALSE)
getSymbols(Symbols = Ticks_09, auto.assing = FALSE)
getSymbols(Symbols = Ticks_10, auto.assing = FALSE)
getSymbols(Symbols = Ticks_11, auto.assing = FALSE)




getSymbols(Symbols = "EVO.ST", auto.assing = FALSE)
getSymbols(Symbols = "ADEN.SW", auto.assing = FALSE)
getSymbols(Symbols = "SWGAY", auto.assing = FALSE)
getSymbols(Symbols = "GSK", auto.assing = FALSE)
getSymbols(Symbols = "ALCN.MX", auto.assing = FALSE)
getSymbols(Symbols = "BEIJ-B.ST", auto.assing = FALSE)
getSymbols(Symbols = "AMUN.PA", auto.assing = FALSE)
getSymbols(Symbols = "MRK.DE", auto.assing = FALSE)
getSymbols(Symbols = "VTAGY", auto.assing = FALSE)
getSymbols(Symbols = "GNS.L", auto.assing = FALSE)
getSymbols(Symbols = "DSRLF", auto.assing = FALSE)

getSymbols(Symbols = "EQT.ST", auto.assing = FALSE)
getSymbols(Symbols = "MRO.L", auto.assing = FALSE)
getSymbols(Symbols = "SXS.L", auto.assing = FALSE)
getSymbols(Symbols = "SDR.L", auto.assing = FALSE)
getSymbols(Symbols = "DOM.ST", auto.assing = FALSE)



getSymbols(Symbols = "TKWY.AS", auto.assing = FALSE)
getSymbols(Symbols = "PRU.DE", auto.assing = FALSE)
getSymbols(Symbols = "LR.PA", auto.assing = FALSE)
getSymbols(Symbols = "LGEN.L", auto.assing = FALSE)
getSymbols(Symbols = "ZAL.DE", auto.assing = FALSE)
getSymbols(Symbols = "NHYDY", auto.assing = FALSE)
getSymbols(Symbols = "NWG", auto.assing = FALSE)
getSymbols(Symbols = "WEIR.L", auto.assing = FALSE)
getSymbols(Symbols = "ATO.PA", auto.assing = FALSE)
getSymbols(Symbols = "0RUG.IL", auto.assing = FALSE)




```

```{r}
raw_stocks_01 <- cbind(`TREL-B.ST`, RR.L, HSV.L, DRX.L, GFC.PA,`0QVM.IL`, AKBLF, `GETI-B.ST`, `SSAB-B.ST`,URW.AS, `0F4I.IL`,DIE.BR, `0GWS.IL`, BOSS.DE, MOWI.OL, TRN.MI, AM.PA, DVDCF,NTGY.MC,OSB.L,ORSTED.CO,MT.AS,DLN.L,RHM.DE,CNA.L,OMV.VI,BLND.L,`TEL2-B.ST`,CAST.ST,ADP.PA,SAFE.L,NESTE.HE,FMS,SCHA.OL,DOCS.L,ADE.OL,PSO,TS,LAND.L,BYG.L,RPYTF, PUB.PA, IFX.DE, COV.PA,`HM-B.ST`, COL.MC, AMS.SW, RTO.L, SDF.DE,GLPEY,AED.BR,IMBBY,ABN.AS,DB1.DE,`0NVV.IL`, SGRO.L, `5PP.F`,ELI.BR,PHP.L,SNMRY,TTE,DUFN.SW,THLLY,NDA.DE,SGBAF,`0RG8.IL`,COFB.BR,AMP.VI,CLLNY,BBOX.L,ARZGY,DEO,III.L,BAYN.DE,TIIAY,WPP,ORK.OL,BESIY,JDSPY,FRE.DE,NXT.L,`0DPU.IL`,`SECT-B.ST`,`0HV2.IL`,IG.VI, AEGOF)
                       
raw_stocks_02 <- cbind(UTG.L,EQNR,KOG.OL,IGG.L,MTX.DE,SHEL,BOL.ST,ACKB.BR,FINMY,WDP.BR,INF.L,TIGO,REPYY,UMG.AS,HELN.SW,RYAAY,KKPNY,`SBB-B.ST`,PSPN.SW,EZJ.L,BAKKA.OL,ENGGY,SOP.PA,RF.PA,SFOR.L,PSM.DE,EXXRF,SALM.OL,CAP.PA,`0R4Y.IL`,ATL.MI,DNOPY,BUD,UMI.BR,NOD.OL,`NETC.CO`,HSX.L,`HOLM-B.ST`,ADYEY,INVP.L,`0N4Y.IL`,FABG.ST,BG.VI,IAG.L,BEI.DE,BTI,RIO,LISN.SW,CA.PA,GLNCY,`0RG6.IL`, AT1.DE, MNG.L, TATE.L,E,`0EWD.IL`,IHG,DTE.DE,`SRT3.DE`,SPSN.SW,`SEB-A.ST`, ORP.PA, DEMANT.CO,DB,VIV.PA,ADS.DE,`SAGA-B.ST`,LUNE.ST,EOAN.DE,NGLOY,KGF.L,ABF.L,ENEL.MI,`SKA-B.ST`,MKS.L,SOBI.ST,KER.PA,TEG.DE,CTEC.L,TEF,`0NMU.IL`,WTB.L,MONRF,BA.L,ORA.VI,`0GWB.IL`,ACXIF,UBS,CDI.PA,SREN.SW,ASML,STM,ITX.VI,BRBY.L,`TELIA1.HE`,`PAH3.DE`,`0MGU.IL`,INDT.ST,CRDA.L,GBLB.BR,`NENT-B.ST`,BP,STMN.SW,`SWED-A.ST`,SFZN.SW,`MUV2.DE`,LIN,NGG,VIFN.SW,ULE.L,`0N54.IL`,BAMI.VI,RSH.HA,`LIFCO-B.ST`,`BALD-B.ST`,ENT.L,KOJAMO.HE,RNO.PA, `BT-A.L`,BVIC.L,VMUK.L,ROG.SW,DCC.L)

raw_stocks_03 <- cbind(WIS.DU,`COLO-B.CO`,LOGI, WIHL.ST, `0RMT.IL`,SGE.L,ALLN.SW, `KINV-B.ST`,UL , RBI.VI, RI.PA,AV.L,SAMPO.HE, LHA.DE,AKZOY, `0RI5.IL`,EMG.L, `0ML1.IL`,`TUI1.DE`,RUBSF, SCHN.SW, SAP , BLHEF, EN.PA, KBCSY, AUTO.OL, `G24.DE`, `0RDV.IL`, STAN.L, `SHB-A.ST` , VOD,SCR.PA, BARN.SW, AKRBP.OL, SPIE.PA, UBI.PA, `SY1.DE`,ELISA.HE, FGR.PA, BUCN.SW, STRN, CFRHF, ALV.DE, ADRNY, NVS, GMAB.CO, `KIND-SDB.ST`, LEG.DE, GALE.SW, CCH.L, EBS.VI,BNZL.L, ERF.PA,BNR.DE,JDE.F,CAIXY, SIGN.SW,TSCO.L,SCMN.SW,`2NN.F`,`0A8B.IL`, ZURN.SW, NEXPF,DG.PA,AI.PA , BOIVF,MC.PA , EDEN.PA, CBK.DE, STERV.HE, RYLPF, CS.PA,ISS.CO,UNCRY, CBG.L,ACS.MC , `ALIF-B.ST`,STLA.PA, `HEXA-B.ST`, `AN3.F`, MBG.DE, `0KBZ.IL`, MGGT.L, AIR.PA, `P9O.F`, PNDORA.CO, SBRY.L, AVST.L, ISP.VI,`0EXG.IL`, CNP.PA, ML.PA, GRG.L, AZN, `HNR1.DE`, SCT.L, ERIC, CS, NOK, LSEG.L, `SK3.IR`, AC.PA, SSE.L, PUM.DE ,EDPFY, CRARY, `LATO-B.ST`, EVK.DE, SWMA.ST,UU.L, `0QVJ.IL`, `BC8.DE`, TECN.SW, WOSG.L, QGEN, LONN.SW)

raw_stocks_04 <- cbind(REC.MI, DKSH.SW, `0NBD.IL`, SNW.DE, IBDRY, ENGI.PA, SOLB.BR, SAF.PA, BBVA, `0QVU.IL`, `ELUX-B.ST`, `SCA-A.ST`, EVO.ST, ADEN.SW, SWGAY, GSK, ALCN.MX, ARCAD.AS, ANDR.VI, HSBC, `0NZM.IL`, HEINY, UPM.HE, ELEZY, TKA.DE, ALLFG.AS, PGHN.SW, ICP.L, TRYG.CO, `INVE-B.ST`, VITR.ST, BCDRF, `0K9W.IL`, MB.MI, INW.MI, DLG.L, SHL.DE, RWE.DE, YAR.OL, TEL.OL, `SWEC-B.ST`,RMG.L, VNA.DE, AGS.BR, OTGLY, DANSKE.CO, AMADY, TEP.PA, SNN, ASM.AS, BKNIY, INCH.L, AAK.ST, ROR.L, SFNXF, `0H13.IL`, HL.L, TYRES.HE, SLHN.SW, STB.OL, BVI.PA, DSV.CO, GET.PA, HLMA.L, HOLN.SW, FNTN.DE , CNHI, WIZZ.L , PNN.L,CON.DE, BEAN.SW, VWAGY, SPX.L , ABDN.L , RMV.L, IWG.L , NSRGY, UCB.BR , BCS , ARKAY , `STOR-B.ST`, RELX, ING, SK.PA, FORTUM.HE, ECM.L, BIRG.IR , `SECU-B.ST`, FUTR.L , RBREW.CO, MNDI.L , BANB.SW, ORNBV.HE, `0HB4.IL`,RACE.VI , WIE.VI,CLN.SW,VWS.CO,`BEIJ-B.ST`, TPK.L , BMW.DE , `0FMN.IL`, CPG.L, SOON.SW , JBAXY,DPW.DE, EXPN.L,AFX.DE,BNDSF, AMUN.PA, MRK.DE, VTAGY,GNS.L, DSRLF, EQT.ST, MRO.L, SXS.L, SDR.L, DOM.ST, `0NY8.IL`,ITV.L,`NZYM-B.CO`,UTDI.DE, `CARL-B.CO`,NEM.DE, BAS.DE, PDYPY, `GL9.IR`,ABB , ITRK.L, SMDS.L, VER.VI, `UN01.DE`, FPE.DE, SGO.VI, `NIBE-B.ST`,SIKA.SW , HAS.L , `0KFX.IL` , `0QP4.IL`, HWDN.L,BEZ.L , `WALL-B.ST`,  IPSEY, DNB.OL,KBX.DE, AHT.L,JMAT.L)

raw_stocks_05 <- cbind(DTG.DE,`AMBU-B.CO`,SGSN.SW, SIM.CO, VOE.VI, ALE.WA, `0RHS.IL`,STJ.L,`HEN3.DE`, PZU.WA, AZA.ST, GFTU.L, CHR.CO, FLUIF, `0RPR.IL`, PRYMY, AALBF, EMSN.SW,PST.MI, SIE.DE, DPH.L, AUTO.L, GLE.VI, ELIS.PA, QLT.L, SW.VI,`EPI-B.ST`, BPT.L, KESKOB.HE, WLN.PA,EVO,`0QVF.IL`,LYG,VLEEY, TKWY.AS, PRU.DE, LR.PA, LGEN.L, ZAL.DE, NHYDY, WEIR.L, NWG, ATO.PA , `0RUG.IL` , NVO, FRRVY, RDSMY , PHNX.L, VCT.L, ADM.L, VACN.SW, KRZ.IR, IMI.L, `HPOL-B.ST`, CRH, GEBN.SW , HEI.DE, EL.PA, BKPKF, GN.CO, `ASSA-B.ST`,BNP.PA, HFG.DE, KHNGF, `ADDT-B.ST`, GIVN.SW, DPLM.L,OCDO.L,KNEBV.HE, VLVLY, BKG.L, EDF.VI,ANTO.L, INRN.SW,`1TY.DE` , `1COV.DE`, LXS.DE,KGHPF , SMIN.L , KRX.IR , EVD.DE, `VOLCAR-B.ST`, `ROCK-B.CO`, MIPS.ST, ENR.DE , LPP.WA, SINCH.ST, BDEV.L, EO.PA, QTCOM.HE, TEMN.SW, ALO.PA, SU.PA, RKT.L, GAW.L, HIK.L, `EKTA-B.ST`,`ESSITY-B.ST`, `HUSQ-B.ST`, FERG, GJF.OL, AVV.L, BMRRY, TW.L, `G1A.DE`, LIGHT.AS, M6Q.SG, DHER.DE, WISE.L, ONT.L, MRSK.VI, KGX.DE, PSN.L, VALMT.HE, ALFA.ST, TOM.OL, SAND.ST, BWY.L, `NDA-FI.HE`, ARGX, VTY.L, ATLC, THULE.ST, SGRE.MC,`SKF-B.ST`, `0IKJ.IL`, RAA.DE)

raw_stocks <- cbind(raw_stocks_01, raw_stocks_02, raw_stocks_03, raw_stocks_04, raw_stocks_05)
```















